On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-04 pps-linear-bound/pps-linear-lower-bound.tex
[J220] A self-found bug

\begin{problem}
	\label{prb:square_side_length_and_diameter_linear}
	What are the maximal numbers $\delta \leq 1$ and $h \leq 0$
	such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in a square of side length $\delta d - h$?
\end{problem}

>>>>

\begin{problem}
	\label{prb:square_side_length_and_diameter_linear}
	What are the minimal numbers $\delta \leq 1$ and $h \leq 0$
	such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in a square of side length $\delta d + h$?
\end{problem}
